The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-02-08 Manuscript/manuscript.tex
Update manuscript.tex
use booktabs package to add horizontal rules; replace 1 with 1.0000; fixed``Z-test'' to be in the same font as in the text

\jy{use booktabs package to add horizontal rules; replace 1 with
  1.0000; make sure ``Z-test'' is in the same font as in the text.}

\begin{table}[tbp]
  \caption{The results from the 9 tests(* denotes significant p-value at alpha=0.05)
  \\*Note: Home and Away scoring totals are divided by 100}
  \label{tab:table}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  & 2020 & 2017--19 & \multicolumn{2}{c}{P-value} & \multicolumn{2}{c}{Adjusted P-value}\\
\cmidrule(lr){4-5}\cmidrule(lr){6-7}
  &          &                & Z-test & Wilcoxon & Z-test & Wilcoxon\\
  \midrule
  Home Win & 0.482 & 0.613 & 0.0497* & 0.0400* & 0.4473 & 0.3598\\
Home Scoring & 1.101 & 1.081 & 0.2321 & 0.2985 & 1 & 1\\
Away Scoring & 1.091 & 1.040 & 0.0008* & 0.0004* & 0.0075* & 0.0035*\\
Home 2P & 0.523 & 0.515 & 0.4335 & 0.5719 & 1 & 1\\
Home 3P & 0.363 & 0.357 & 0.5733 & 0.8852 & 1 & 1\\
Home FT & 0.793 & 0.774 & 0.0692 & 0.0496* & 0.6228 & 0.4464\\
Away 2P & 0.536 & 0.504 & 0.0003* & 0.0003* & 0.0030 & 0.0023\\
Away 3P & 0.357 & 0.346 & 0.3256 & 0.3081 & 1 & 1\\
Away FT & 0.783 & 0.777 & 0.6601 & 0.8370 & 1 & 1\\
  \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[tbp]
  \caption{The results from the 9 tests(* denotes significant p-value at alpha=0.05)
  \\*Note: Home and Away scoring totals are divided by 100}
  \label{tab:table}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  & 2020 & 2017--19 & \multicolumn{2}{c}{P-value} & \multicolumn{2}{c}{Adjusted P-value}\\
\cmidrule(lr){4-5}\cmidrule(lr){6-7}
  &          &                & \(Z\)-test & Wilcoxon & \(Z\)-test & Wilcoxon\\
  \midrule
  Home Win & 0.482 & 0.613 & 0.0497* & 0.0400* & 0.4473 & 0.3598\\
  \midrule
Home Scoring & 1.101 & 1.081 & 0.2321 & 0.2985 & 1.0000 & 1.0000\\
\midrule
Away Scoring & 1.091 & 1.040 & 0.0008* & 0.0004* & 0.0075* & 0.0035*\\
\midrule
Home 2P & 0.523 & 0.515 & 0.4335 & 0.5719 & 1.0000 & 1.0000\\
\midrule
Home 3P & 0.363 & 0.357 & 0.5733 & 0.8852 & 1.0000 & 1.0000\\
\midrule
Home FT & 0.793 & 0.774 & 0.0692 & 0.0496* & 0.6228 & 0.4464\\
\midrule
Away 2P & 0.536 & 0.504 & 0.0003* & 0.0003* & 0.0030 & 0.0023\\
\midrule
Away 3P & 0.357 & 0.346 & 0.3256 & 0.3081 & 1.0000 & 1.0000\\
\midrule
Away FT & 0.783 & 0.777 & 0.6601 & 0.8370 & 1.0000 & 1.0000\\
  \bottomrule
\end{tabular}
\end{table}
